### 2019-11-25 paper/results.tex

\section{Results and discussion} \label{Results-and-discussion}
The molar fraction of the heavy metal (HM) 
in the initial fuel was kept constant and equal to 12.5 mole\% for all cases (see Table~\ref{tab:table4}). 
Additionally, the initial fissile material fraction was increased for the five fuel 
salt compositions until the \gls{SD-TMSR} reactor was sufficiently critical at 
the Beginning Of Life (BOL).
\subsection{Thorium feed mechanism}
The thorium feed mechanism continuously feeds thorium from the external stockpile and 
$^{233}$U from the \texttt{Pa-decay tank}.
Figure~\ref{fig:keff1} illustrates the effective multiplication factor 
dynamics during reactor operation for the thorium feed mechanism. As shown in 
Figure~\ref{fig:keff1}, the effective multiplication factor ($k_{eff}$) 
decreases sharply during the first 25 \gls{EFPY} of reactor operation for the first 
four cases. $k_{eff}$ decreases as a result of depletion of the initial 
fissile materials and production of poisonous fission products (FPs). The amount of $^{233}$U generated in 
the SD-TMSR is not enough to maintain the reactor criticality and 
counteract parasitic neutron absorption. Thus, the 
reactor becomes subcritical relatively quickly for alternative startup 
compositions, for example, $\approx$ $4$ years in the \gls{TRU} case and $\approx$ $12$ 
years in the reactor-grade Pu case. For U-233 case, 
the continuous feed flow of thorium and $^{233}$U from the \texttt{Pa-decay tank} helps to operate the 
\gls{SD-TMSR} for a full lifetime (60 year) (Figure~\ref{fig:keff1} (U-233 case)). 
Additionally, the molar fractions of \gls{HALEU} and reactor-grade Pu in the initial fuel composition were increased
more. Consequently, the initial $k_{eff}$ for these cases increased (Figure~\ref{fig:keff1} (HALEU and reactor-grade Pu cases)). Nevertheless, $k_{eff}$ still decreases below 1.0, as a result of increasing the non-fissile heavy metals in the initial fuel \cite{betzler2016modeling}.

>>>>

\section{Results and discussion} \label{Results-and-discussion}
The molar fraction of the heavy metal (HM) 
in the initial fuel was kept constant and equal to 12.5 mole\% for all cases (see Table~\ref{tab:table4}). 
Additionally, the initial fissile material fraction was increased for the five fuel 
salt compositions until the \gls{SD-TMSR} reactor was sufficiently critical at 
the Beginning Of Life (BOL).
\subsection{Thorium feed mechanism}
The thorium feed mechanism continuously feeds thorium from the external stockpile and 
$^{233}$U from the \texttt{Pa-decay tank}.
Figure~\ref{fig:keff1} illustrates the effective multiplication factor 
dynamics during reactor operation for the thorium feed mechanism. As shown in 
Figure~\ref{fig:keff1}, the effective multiplication factor ($k_{eff}$) 
decreases sharply during the first 25 \gls{EFPY} of reactor operation for the first 
four cases. $k_{eff}$ decreases as a result of depletion of the initial 
fissile materials and production of poisonous fission products (FPs). The amount of $^{233}$U generated in 
the SD-TMSR is not enough to maintain the reactor criticality and 
counteract parasitic neutron absorption. Thus, the 
reactor becomes subcritical relatively quickly for alternative startup 
compositions, for example, $\approx$ $4$ years in the \gls{TRU} case and $\approx$ $12$ 
years in the reactor-grade Pu case. For U-233 case, 
the continuous feed flow of thorium and $^{233}$U from the \texttt{Pa-decay tank} helps to operate the 
\gls{SD-TMSR} for a full lifetime (60 year) (Figure~\ref{fig:keff1} (U-233 case)). 
Additionally, the molar fractions of \gls{HALEU} and reactor-grade Pu in the initial fuel composition were increased
more. Consequently, the initial $k_{eff}$ for these cases increased (Figure~\ref{fig:keff1} (HALEU and reactor-grade Pu cases)). But the produced $^{233}$U is insufficient to keep the reactor critical and counteract parasitic neutron absorption. Therefore, $k_{eff}$ is decreased below 1.0, after $\approx$ $6$ years in the HALEU case and $\approx$ $12$ years in the reactor-grade Pu case.
